The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-06 paper/ms.tex
more text into past tense

While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. From the 34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters as through these scaling relations:

@@

We follow the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}. We then conduct a Markov Chain Monte Carlo fit to this, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}, consisting of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise. We find that the marginal posterior distribution for the Gaussian envelope is well-approximated by a single Gaussian, and take its median and standard deviation to be our estimates for \numax and its uncertainty.

To estimate \Dnu, we divide the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

We obtain good estimates of these asteroseismic parameters for 35 targets, presented in Table~\ref{astero_table}. In many of the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.

Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.

For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.

To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and chemical abundances for 20 chemical species are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}. For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation). Additionally we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T. Masseron, private communication). The SiH molecular information is adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B. Plez (private communication).

>>>>

While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters as through these scaling relations:

@@

We have followed the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}. The posterior distribution of the asteroseismic parameters is obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}. This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise. The marginal posterior distribution for the oscillation envelope is well-approximated by a single Gaussian, and we have taken its median and standard deviation to be our estimates for \numax and its uncertainty.

To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

We obtain good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}. In the remainder of cases, as noted above, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.

Once \numax has been estimated, we have used the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.

For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element. This resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values. The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and chemical abundances for 20 chemical species are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}. BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}. For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation). Additionally we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T. Masseron, private communication). The SiH molecular information is adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B. Plez (private communication).
